%%% Author: mterenui (F.M.T.C)
%%% Docs: https://github.com/xxx
%%% License: GNU General Public License v3.0
%%% This document is provided as a general template for informational purposes only and does not constitute legal advice. Permission is granted to copy, modify, and use this template for personal or commercial purposes, provided that this copyright and license notice is retained in all copies or substantial portions of the document. The author makes no representations or warranties regarding the legal validity or enforceability of this template in any jurisdiction. Users are strongly encouraged to consult a qualified legal professional before using this document.

\section{Distribution of Assets}
\label{sec:assets}

\subsection{Immovable Property}
I hereby give, devise, and bequeath absolutely and forever my immovable property described below to the following beneficiaries in the proportions stated below (hereinafter collectively referred to as “\textit{the Beneficiary}”):

\begin{itemize}
  \item \FirstBeneficiaryName{}, \FirstBeneficiaryRelationship{}, shall receive \FirstBeneficiaryFraction{} of my Immovable Property.
  \item \SecondBeneficiaryName{}, \SecondBeneficiaryRelationship{}, shall receive \SecondBeneficiaryFraction{} of my Immovable Property.
  \item \ThirdBeneficiaryName{}, \ThirdBeneficiaryRelationship{}, shall receive \ThirdBeneficiaryFraction{} of my Immovable Property.
\end{itemize}

\subsubsection*{Property Description}
The immovable property (hereinafter referred to as “\textit{the said Property}”) consists of:

\vspace{0.2cm}

\noindent
\begin{tabular}{p{8cm} p{8cm}}
\textbf{Type of Property:} & \PropertyType{} \\ 
\textbf{Full Address:} & \PropertyAddress{} \\ 
\textbf{Place:} & \PropertyLocation{} \\ 
\textbf{Title Deed Reference:} & \PropertyDeed{} \\ 
\end{tabular}

\subsubsection*{Rights Conveyed}
Each Beneficiary shall, upon my demise, receive their respective share absolutely and become the sole and absolute owner of the said Property with full rights of ownership, possession, use and enjoyment, sale, gift, lease, mortgage or transfer without any restriction whatsoever.

\subsubsection*{Encumbrances and Liabilities}
If any loan, charge, tax, maintenance dues, or other liabilities exist on the said Property at the time of my death, the same shall be cleared from my estate. 

\subsubsection*{Vacant Possession}
I direct that vacant and peaceful possession of the said Property shall be handed over to the Beneficiary as soon as practicable after my demise, subject to completion of legal formalities.

\subsubsection*{Declaration of Title}
I declare that the said Property is my self-acquired property and that I have full legal authority to dispose of it through this Will.

\subsection{Movable Assets}
I hereby give and bequeath all my movable assets, whether tangible or intangible, owned by me at the time of my death, to to the following beneficiaries in the proportions stated below (hereinafter collectively referred to as “\textit{the Beneficiary}”), subject to the terms stated herein.

\begin{itemize}
  \item \FirstBeneficiaryName{}, \FirstBeneficiaryRelationship{}, shall receive \FirstBeneficiaryFraction{} of my Movable Assets.
  \item \SecondBeneficiaryName{}, \SecondBeneficiaryRelationship{}, shall receive \SecondBeneficiaryFraction{} of my Movable Assets.
  \item \ThirdBeneficiaryName{}, \ThirdBeneficiaryRelationship{}, shall receive \ThirdBeneficiaryFraction{} of my Movable Assets.
\end{itemize}

\subsubsection*{Scope of Movable Assets}
For the purpose of this Will, “\textit{movable assets}” shall include, but not be limited to:

\begin{itemize}
  \item Cash in hand
  \item Bank balances in savings, current, fixed deposit, or recurring deposit accounts
  \item Investments such as shares, mutual funds, bonds, debentures, provident funds, pension accounts, and insurance proceeds
  \item Vehicles, including cars, two-wheelers, and other motor vehicles
  \item Jewelry, precious metals, ornaments, and valuables
  \item Furniture, appliances, electronics, and household effects
  \item Business interests, partnership shares, or sole proprietorship asset
  \item Digital assets, including online accounts, wallets, and intellectual property (where permitted by law)
\end{itemize}

\subsubsection*{Distribution and Ownership}
Each Beneficiary shall, upon my demise, receive their respective share absolutely and become the absolute owner of the movable assets received in the context of this Will with full rights to possess, use, operate, transfer, sell, or otherwise dispose of the same in any lawful manner.

\vspace{0.2 cm}

\noindent Unless expressly stated otherwise, no asset shall be held jointly, and each beneficiary’s share shall be treated as separate and independent.

\subsubsection*{Specific Bequests}
Notwithstanding the above, I may have made specific bequests of certain movable assets as follows:

\vspace{0.3cm}

\noindent
\begin{tabular}{p{8cm} p{8cm}}
\textbf{Description of Asset} & \FirstBeneficiaryName{} \\ 
\textbf{Description of Asset} & \SecondBeneficiaryName{} \\ 
\end{tabular}

\subsubsection*{Encumbrances and Liabilities}
Any outstanding loans, dues, or charges relating to the movable assets shall be cleared from my estate as applicable. 

\subsubsection*{Declaration}
I declare that the movable assets bequeathed under this clause are owned by me lawfully and that I have full right and authority to dispose of the same through this Will.

\subsection{Residual Estate}
I give all the rest, residue, and remainder of my estate to \FirstBeneficiaryName{}.

%%% End of document (assets.tex)